Unveiling Exception Handling Bug Hazards in Android based on GitHub and Google Code Issues

### 2015-03-27 android-stacks.tex
results section

This section presents the results of the study, this presentation is centered around parts 
of exception stack traces (i.e., the root exceptions, the exception types, 
and the exception wrappings).  Each part is then analyzed in detail to 
check whether they can reveal bug harzards on the exception handling code
related or not to violations of the best practices presented
 in Section~\ref{sec:best}.

>>>>

This section presents the results of the study, this presentation is centered around 
characteristics distilled from stack traces: (i) the root exceptions, (ii) the exception types, 
and (iii) the exception wrappings.  Each part is then analyzed in detail to 
check whether they can reveal bug harzards on the exception handling code
related or not to violations of the best practices presented
 in Section~\ref{sec:best}.
